Universal relations after GW170817

### 2018-12-18 paper/bin-love-after-gw170817.tex
small changes from Kents email

\begin{table}
\centering
\caption{
Comparison between the universal relations (both I-Love-Q and binary Love) maximal EoS variability for the results of previous works~\cite{Yagi:ILQ,Yagi:binLove}, and the unconstrained and constrained sets of EoSs analyzed here. 
The maximum EoS variation, given by the largest fractional difference from the fits as shown in Figs.~\ref{fig:ILQ} and~\ref{fig:binLove}, sees a considerable improvement for the constrained set of EoSs, compared to the unconstrained set as well as previous works.
Additionally, notice how the maximal EoS variation for the unconstrained set of EoSs is slightly higher than that found in Refs.~\cite{Yagi:ILQ,Yagi:binLove} - due to the effects of large random sampling taking into account more sources of uncertainty.\zc{Kent do you know the IQ max EoS variation? It's not quoted or shown in the paper}
}\label{tab:maxVar}
\begin{tabular}{ c  || c c c } 
 \hline
 \hline
 \textbf{Universal} & \multicolumn{3}{c}{\textbf{Maximal EoS Variability}} \\
 \cline{2-4}
 \textbf{Relation} & \multicolumn{1}{c|}{\emph{Previous}} & \multicolumn{1}{c|}{\emph{Unconstrained}} & \emph{Constrained}\\
 \hline
 $\bar{I}-\Lambda$ & $\sim 0.005$ & $0.0076725$ & $0.0031383$\\
 $\bar{Q}-\Lambda$ & $\sim 0.009$ & $0.012617$ & $0.0046612$\\
 $\bar{I}-\bar{Q}$ & ? & $0.014895$ & $0.0057157$\\
 \hline
 $\Lambda_a-\Lambda_s$ & \multirow{2}{*}{$\sim0.50$} & \multirow{2}{*}{$0.5723891$} & \multirow{2}{*}{$0.2140192$}\\
 $(q=0.90)$ & & &\\
 \cline{1-1}
 $\Lambda_a-\Lambda_s$ & \multirow{2}{*}{$\sim0.20$} & \multirow{2}{*}{$0.2447418$} & \multirow{2}{*}{$0.0828446$}\\
  $(q=0.7)$ & & &\\
  \cline{1-1}
 $\Lambda_a-\Lambda_s$ & \multirow{2}{*}{$\sim0.025$} & \multirow{2}{*}{$0.0384088$} & \multirow{2}{*}{$0.0182308$}\\
  $(q=0.50)$ & & &\\
  \cline{1-1}
\hline
\hline
\end{tabular}
\end{table}

@@

\begin{figure}
\begin{center} 
\includegraphics[width=\linewidth]{binLove.eps}
\end{center}
\caption{
Binary Love universal relations shown for the constrained EoSs (dotted maroon) and unconstrained EoSs (solid green) for various values of mass ratio: $q=0.9$, $q=0.75$, and $q=0.50$.
In this figure, the top panel displays the universal relations with fits given by Eq.~\ref{eq:binLovefit} shown by dashed black lines, while the bottom 3 panels correspond to the EoS variation for each mass ratio.
Observe how the the constrained set of EoSs show a reduction in EoS variation for both the unconstrained set, and from the results shown in Ref.~\cite{Yagi:binLove}.
The max EoS variability for each case is tabulated and compared in Tab.~\ref{tab:maxVar}.
Additionally shown is the binary Love relations for the 10 hybrid star EoSs (dashed green curves) as discussed in Sec.~\ref{sec:binLove-hybrid}.
Observe the large deviations from the fit as the mass ratio $q$ increases, returning near the fit before the transitional pressure at large values of $\Lambda_s$.
}
\label{fig:binLove}
\end{figure}

@@

To further investigate this phenomena, we consider binary Love fits to the HS branches, or NS branches \emph{individually}.
It was found that by trying to fit binary Love relations to the full hybrid star EoSs failed, due to the difference in transitional masses $M_{\text{tr}}$.
To compensate for these differences, we separate the two branches into the NS (hadronic matter) and HS (hybrid matter) branches.
We first observe that the NS branch obeys the ``hadronic" binary Love relations derived earlier in Sec.~\ref{sec:binLove-nuclear} within the variability found earlier, indicating no further need for additional fits.
However, the HS branch does not, suggesting the need for a new ``hybrid" binary love fit pertaining to this branch.
We begin by fitting the binary Love relations to the new HS branch, resulting in the fit coefficients found in the bottom row of Tab.~\ref{tab:binLovefit}.
We urge caution with the use of these fits, as the small sample size (10 EoSs) as well as the occurrence of hybrid matter transitions only being available for certain mass ratios on certain EoSs, results in a less accurate fit than the nuclear-matter counterpart.
Similar to before, the fractional difference from the fit for each HS branch is computed, resulting in a maximum variability of $18.488$\% for $q=0.90$.
This result is strongly consistent with the results found for the nuclear matter fits of Sec.~\ref{sec:binLove-nuclear}.

>>>>

\begin{table}
\centering
\caption{
Comparison between the universal relations (both I-Love-Q and binary Love) maximal EoS variability for the results of previous works~\cite{Yagi:ILQ,Yagi:binLove}, and the unconstrained and constrained sets of EoSs analyzed here. 
The maximum EoS variation, given by the largest fractional difference from the fits as shown in Figs.~\ref{fig:ILQ} and~\ref{fig:binLove}, sees a considerable improvement for the constrained set of EoSs, compared to the unconstrained set as well as previous works.
Additionally, notice how the maximal EoS variation for the unconstrained set of EoSs is slightly higher than that found in Refs.~\cite{Yagi:ILQ,Yagi:binLove} - due to the effects of large random sampling taking into account more sources of uncertainty.
}\label{tab:maxVar}
\begin{tabular}{ c  || c c c } 
 \hline
 \hline
 \textbf{Universal} & \multicolumn{3}{c}{\textbf{Maximal EoS Variability}} \\
 \cline{2-4}
 \textbf{Relation} & \multicolumn{1}{c|}{\emph{Previous}} & \multicolumn{1}{c|}{\emph{Unconstrained}} & \emph{Constrained}\\
 \hline
 $\bar{I}-\Lambda$ &  $0.0059$ & $0.0076725$ & $0.0031383$\\
 $\bar{Q}-\Lambda$ & $0.0010$ & $0.012617$ & $0.0046612$\\
 $\bar{I}-\bar{Q}$ & $0.012$ & $0.014895$ & $0.0057157$\\
 \hline
 $\Lambda_a-\Lambda_s$ & \multirow{2}{*}{$\sim0.50$} & \multirow{2}{*}{$0.5723891$} & \multirow{2}{*}{$0.2140192$}\\
 $(q=0.90)$ & & &\\
 \cline{1-1}
 $\Lambda_a-\Lambda_s$ & \multirow{2}{*}{$\sim0.20$} & \multirow{2}{*}{$0.2447418$} & \multirow{2}{*}{$0.0828446$}\\
  $(q=0.7)$ & & &\\
  \cline{1-1}
 $\Lambda_a-\Lambda_s$ & \multirow{2}{*}{$\sim0.025$} & \multirow{2}{*}{$0.0384088$} & \multirow{2}{*}{$0.0182308$}\\
  $(q=0.50)$ & & &\\
  \cline{1-1}
\hline
\hline
\end{tabular}
\end{table}

@@

\begin{figure}
\begin{center} 
\includegraphics[width=\linewidth]{binLove.eps}
\end{center}
\caption{
Binary Love universal relations shown for the constrained EoSs (dotted maroon) and unconstrained EoSs (solid green) for various values of mass ratio: $q=0.9$, $q=0.75$, and $q=0.50$.
In this figure, the top panel displays the universal relations with fits given by Eq.~\ref{eq:binLovefit} shown by dashed black lines (note there are 2 fits for each mass ratio, corresponding to the constrained and unconstrained sets of EoSs), while the bottom 3 panels correspond to the EoS variation for each mass ratio.
Observe how the the constrained set of EoSs show a reduction in EoS variation for both the unconstrained set, and from the results shown in Ref.~\cite{Yagi:binLove}.
The max EoS variability for each case is tabulated and compared in Tab.~\ref{tab:maxVar}.
Additionally shown is the binary Love relations for the 10 hybrid star EoSs (dashed bright green curves), as well as the HS fits (dot-dashed blue curves) discussed in Sec.~\ref{sec:binLove-hybrid}.
Observe the large deviations from the fit as the mass ratio $q$ increases, returning near the fit before the transitional pressure at large values of $\Lambda_s$.
This is shown in the bottom three panels as the fractional difference from the NS fit for comparison, while the HS fits show similar EoS variability to the constrained EoSs.
}
\label{fig:binLove}
\end{figure}

@@

To further investigate this phenomena, we consider binary Love fits to the HS branches, or NS branches \emph{individually}.
It was found that by trying to fit binary Love relations to the full hybrid star EoSs failed, due to the difference in transitional masses $M_{\text{tr}}$.
To compensate for these differences, we separate the two branches into the NS (hadronic matter) and HS (hybrid matter) branches.
We first observe that the NS branch obeys the ``hadronic" binary Love relations derived earlier in Sec.~\ref{sec:binLove-nuclear} within the variability found earlier, indicating no further need for additional fits.
However, the HS branch does not, suggesting the need for a new ``hybrid" binary love fit pertaining to this branch.
We begin by fitting the binary Love relations to the new HS branch, resulting in the fit coefficients found in the bottom row of Tab.~\ref{tab:binLovefit}.
The fits are displayed in the top panel of Fig.~\ref{fig:binLove} as dot-dashed blue curves, showing a good relationship with the hybrid star branch.
We urge caution with the use of these fits, as the small sample size (10 EoSs) as well as the occurrence of hybrid matter transitions only being available for certain mass ratios on certain EoSs, results in a less accurate fit than the nuclear-matter counterpart.
Similar to before, the fractional difference from the fit for each HS branch is computed, resulting in a maximum variability of $18.488$\% for $q=0.90$.
This result is strongly consistent with the results found for the nuclear matter fits of Sec.~\ref{sec:binLove-nuclear}.
